Hello OpenScPCA

### 2024-03-16 analyses/hello-R/notebooks/hello.Rmd
start to respond to review

---
title: "Hello OpenScPCA"
output: html_notebook
---

@@

### Setup

@@

```{r setup}
# load required libraries
suppressPackageStartupMessages({
  library("SingleCellExperiment")
  library("ggplot2")
})

# Find the repository root
repo_root <- rprojroot::find_root(rprojroot::is_git_root)

@@

# set results and plots directories (using the analysis project file to find root)
results_dir <- here::here("results")
plots_dir <- here::here("plots")
```

@@

>>>>

---
title: Hello OpenScPCA
author:
  - Joshua A. Shapiro, Childhood Cancer Data Lab, ALSF
date: "`r Sys.Date()`"
output: html_notebook
---

@@

## Setup

@@

```{r libraries}
# load required libraries
suppressPackageStartupMessages({
  library("SingleCellExperiment")
  library("ggplot2")
})
```

Set the paths to the data, results, and plots directories.

```{r}
# Find the repository and module root directories
repo_root <- rprojroot::find_root(rprojroot::is_git_root)
module_root <- rprojroot::find_root(rprojroot::is_renv_project)

@@

# set results and plots directories (using the analysis project file to find root)
results_dir <- file.path(module_root, "results")
plots_dir <- file.path(module_root, "plots")
```

@@

## Session Info

```{r}
sessioninfo::session_info()
```
